---
title: Align sumstats with RICOPILI pipeline
author: Mark Adams
---

Sumstats from Generation Scotland need to be [aligned with the PGC imputation panel](https://docs.google.com/document/d/1o4bN_uLK4IEItXCSdeQkXfZwEpLuSCWlveJevRogi08/) (1KG).  

```{r}

library(readr)
library(dplyr)

daner <- read_tsv('daner_mdd_genscot_1119a_rmUKBB.gz')

```

List and load alignments files. The document suggests pulling from files with the suffix `*.EUR.frq2.gz` but these do not exist for the circa 2012 imputation files that were used for **MDD2**, so instead we open the `*.eur.bfile.bim` files.

```{r}

eur_bim_files <- 
list.files('/home/gwas/pgc-samples/hapmap_ref/impute2_ref/1KG_Aug12/ALL_1000G_phase1integrated_v3_impute_macGT1/', pattern="my.ALL_1000G_phase1integrated_v3_aug2012_macGT1_chr.+\\.eur\\.bfile\\.bim", full.names=TRUE)

# specify column times i=integer, c=character
eur_bim <- bind_rows(lapply(eur_bim_files, read_table2, col_names=c('CHR', 'snpid', 'CM', 'BP', 'A1', 'A2'), col_types='iciicc'))

```

Merge sumstats on CPIDs `CHR_POS_A1_A2` and `CHR_POS_A2_A1` 

```{r}

daner_cpid <-
bind_rows(
daner %>% 
  inner_join(eur_bim, by=c('CHR'='CHR', 'BP'='BP', 'A1'='A1', 'A2'='A2')),
daner %>% 
  inner_join(eur_bim, by=c('CHR'='CHR', 'BP'='BP', 'A1'='A2', 'A2'='A1'))
)

```

Number of sites with differerent RSIDs
```{r}

daner_cpid %>%
filter(SNP != snpid) %>%
tally()

```

Unmatched sites

```{r}

daner_cpid_nomatch <-
daner %>%
anti_join(daner_cpid, by=c('CHR', 'SNP'))

```

Update SNP ID

```{r}

daner_aligned <-
daner_cpid %>%
select(CHR, SNP=snpid, BP, A1, A2, starts_with('FRQ'), INFO, OR, SE, P, ngt) %>%
bind_rows(daner_cpid_nomatch) %>%
arrange(CHR, BP)

```

```{r}

write_tsv(daner_aligned, 'daner_mdd_genscot_1119a_rmUKBB.aligned.gz')

```
